### 2019-05-29 doc/chapters/towards_verifying_addition.tex
small font size for verbatim

\section{Rewriting Abstract Type Member}
Stainless output:
\begin{verbatim}
[ Error  ] CurrencyUnits.scala:5:3: Stainless doesn't support abstract type members
           type A
\end{verbatim}
This should be easy to rewrite by using generics instead of an abstract type, right?
Unfortunately not.
The problem is, CurrencyUnit uses its implementing class Satoshis.

@@

\section{Rewriting Generics}
Stainless output:
\begin{verbatim}
  [ Error  ] NumberType.scala:3:30: Unknown type parameter type T
             sealed abstract class Number[T <: Number[T]]
\end{verbatim}

@@

\section{Rewriting Objects}
Stainless output:
\begin{verbatim}
[ Error  ] CurrencyUnits.scala:54:1: Objects cannot extend classes or implement
           traits, use a case object instead
           object Satoshis extends BaseNumbers[Satoshis] {
\end{verbatim}

@@

\section{Rewriting BigInt Constructor (only literal argument, no long argument, etc.)}
Stainless output:
\begin{verbatim}
[ Error  ] CurrencyUnits.scala:47:33: Only literal arguments are allowed for BigInt.
           def toBigInt: BigInt = BigInt(toLong)
\end{verbatim}

@@

\section{Rewriting Private Inner Classes}
Stainless output (simplified):
\begin{verbatim}
  [Warning ] CurrencyUnits.scala:36:3: Could not extract tree in class:
             case private class SatoshisImpl extends Satoshis
\end{verbatim}

@@

\section{Rewriting Type Member}
Stainless output:
\begin{verbatim}
  [Warning ] NumberType.scala:5:3: Could not extract tree in class: type A
             = BigInt (class scala.reflect.internal.Trees$TypeDef)
             type A = BigInt
\end{verbatim}

@@

\section{Rewriting Usage of BigInt \&-Function}
Stainless output:
\begin{verbatim}
  [ Error  ] NumberType.scala:19:14: Unknown call to & on result (BigInt) with
             arguments List(Number.this.andMask) of type List(BigInt)
             require((result & andMask) == result,
\end{verbatim}

@@

\section{Rewriting require}
Stainless output:
\begin{verbatim}
  [Warning ] NumberType.scala:54:3: Could not extract tree in class:
             scala.this.Predef.require(Int64Impl.this.underlying.<=(
             math.this.BigInt.long2bigInt(9223372036854775807L)),
             "Number was too big for a int64, got: ".+(Int64Impl.this.underlying))
             (class scala.reflect.internal.Trees$Apply)
             require(underlying <= 9223372036854775807L,
\end{verbatim}

@@

Stainless output:
\begin{verbatim}
  [Warning ] Found counter-example:
  [Warning ]   thiss: { x: Object | @unchecked isNumber(x) } -> Int64Impl(0)
  [Warning ]   num: { x: Object | @unchecked isInt64(x) }    -> 
                 Int64Impl(9223372036854775808)
\end{verbatim}

@@

Stainless finds another counter example:
\begin{verbatim}
  [Warning ] Found counter-example:
  [Warning ]   num: { x: Object | @unchecked isInt64(x) }    -> Int64Impl(1)
  [Warning ]   thiss: { x: Object | @unchecked isNumber(x) } ->
                 Int64Impl(9223372036854775807)
\end{verbatim}

>>>>

\section{Rewriting Abstract Type Member}
Stainless output:
{\footnotesize\begin{verbatim}
[ Error  ] CurrencyUnits.scala:5:3: Stainless doesn't support abstract type members
           type A
\end{verbatim}}
This should be easy to rewrite by using generics instead of an abstract type, right?
Unfortunately not.
The problem is, CurrencyUnit uses its implementing class Satoshis.

@@

\section{Rewriting Generics}
Stainless output:
{\footnotesize\begin{verbatim}
  [ Error  ] NumberType.scala:3:30: Unknown type parameter type T
             sealed abstract class Number[T <: Number[T]]
\end{verbatim}}

@@

\section{Rewriting Objects}
Stainless output:
{\footnotesize\begin{verbatim}
[ Error  ] CurrencyUnits.scala:54:1: Objects cannot extend classes or implement
           traits, use a case object instead
           object Satoshis extends BaseNumbers[Satoshis] {
\end{verbatim}}

@@

\section{Rewriting BigInt Constructor (only literal argument, no long argument, etc.)}
Stainless output:
{\footnotesize\begin{verbatim}
[ Error  ] CurrencyUnits.scala:47:33: Only literal arguments are allowed for BigInt.
           def toBigInt: BigInt = BigInt(toLong)
\end{verbatim}}

@@

\section{Rewriting Private Inner Classes}
Stainless output (simplified):
{\footnotesize\begin{verbatim}
  [Warning ] CurrencyUnits.scala:36:3: Could not extract tree in class:
             case private class SatoshisImpl extends Satoshis
\end{verbatim}}

@@

\section{Rewriting Type Member}
Stainless output:
{\footnotesize\begin{verbatim}
  [Warning ] NumberType.scala:5:3: Could not extract tree in class: type A
             = BigInt (class scala.reflect.internal.Trees$TypeDef)
             type A = BigInt
\end{verbatim}}

@@

\section{Rewriting Usage of BigInt \&-Function}
Stainless output:
{\footnotesize\begin{verbatim}
  [ Error  ] NumberType.scala:19:14: Unknown call to & on result (BigInt) with
             arguments List(Number.this.andMask) of type List(BigInt)
             require((result & andMask) == result,
\end{verbatim}}

@@

\section{Rewriting require}
Stainless output:
{\footnotesize\begin{verbatim}
  [Warning ] NumberType.scala:54:3: Could not extract tree in class:
             scala.this.Predef.require(Int64Impl.this.underlying.<=(
             math.this.BigInt.long2bigInt(9223372036854775807L)),
             "Number was too big for a int64, got: ".+(Int64Impl.this.underlying))
             (class scala.reflect.internal.Trees$Apply)
             require(underlying <= 9223372036854775807L,
\end{verbatim}}

@@

Stainless output:
{\footnotesize\begin{verbatim}
  [Warning ] Found counter-example:
  [Warning ]   thiss: { x: Object | @unchecked isNumber(x) } -> Int64Impl(0)
  [Warning ]   num: { x: Object | @unchecked isInt64(x) }    -> 
                 Int64Impl(9223372036854775808)
\end{verbatim}}

@@

Stainless finds another counter example:
{\footnotesize\begin{verbatim}
  [Warning ] Found counter-example:
  [Warning ]   num: { x: Object | @unchecked isInt64(x) }    -> Int64Impl(1)
  [Warning ]   thiss: { x: Object | @unchecked isNumber(x) } ->
                 Int64Impl(9223372036854775807)
\end{verbatim}}
